---
title: "Lijia Yu's resume"
author: Lijia Yu
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: 
      - css/custom_resume.css
      - css/styles.css
      - resume
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)

# ======================================================================
# These variables determine how the the data is loaded and how the exports are
# done.

# Is data stored in google sheets? If no data will be gather from the csvs/
# folder in project
using_googlesheets <- FALSE

# Just the copied URL from the sheet
positions_sheet_loc <- "https://docs.google.com/spreadsheets/d/14MQICF2F8-vf8CKPF1m4lyGKO6_thG-4aSwat1e2TWc"

# Is this sheet available for anyone to read? If you're using a private sheet
# set this to false and go to gather_data.R and run the data loading manually
# once to cache authentication
sheet_is_publicly_readable <- TRUE

# Is the goal of this knit to build a document that is exported to PDF? If so
# set this to true to have links turned into footnotes at the end of the
# document
PDF_EXPORT <- FALSE


# A global (gasp) variable that holds all the links that were inserted for
# placement at the end
links <- c()

# ======================================================================
# Now we source two external scripts. One contains functions for building the
# text output and the other loads up our data from either googlesheets or csvs

# Functions for building sections from CSV data
source('parsing_functions.R') 

# Load data for CV/Resume
source('gather_data.R')

# Now we just need to filter down the position data to include less verbose
# categories and only the entries we have designated for the resume
position_data <- position_data %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('research_positions', 'industry_positions') ~ 'positions', 
      section %in% c('data_science_writings', 'by_me_press') ~ 'writings',
      TRUE ~ section
    )
  ) 
```



Aside
================================================================================


![Lijia Yu](https://avatars1.githubusercontent.com/u/895125?s=400&v=4){width=80%}


Contact Info {#contact}
--------------------------------------------------------------------------------

```{r}
contact_info %>% 
  glue_data("- <i class='fa fa-{icon}'></i> {contact}")
```
- For more information, please contact me via email.


Skills {#skills}
--------------------------------------------------------------------------------

```{r}
build_skill_bars(skills)
```

Experienced in statistical analysis, statistical learning models, and optimization methods.

Full experience with next generation sequencing data analysis.


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`.



Main
================================================================================

Lijia Yu {#title}
--------------------------------------------------------------------------------

### Currently searching for a PhD student position

```{r}
print_text_block(text_blocks, 'intro')
```


Education {data-icon=graduation-cap}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('education')
```


Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('research')
```


Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------


```{r}
position_data %>% print_section('industry')
```


Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

### Introduction to R Language for Beginners.

Instructor of R and Data Mining Training Courses at SupStat Inc.

Beijing, China

2014

### Computational Biology and Bioinformatics.

Teaching assistant of GBS CB2-201 courses at UAB

AL, USA

2016 - 2017


Selected Publications and Posters {data-icon=file}
--------------------------------------------------------------------------------

### Genetic and epigenetic signals are found predictive to the distribution of intra-individual divergence of alternative splicing.

Poster for 2013 International Conference of Genomics

Qingdao, China

2014

**Yu L**, Chen B, Zhang Z.

### ESCRT-0 complex modulates Rbf mutant cell survival by regulating Rhomboid endosomal trafficking and EGFR signaling.

J Cell Sci. 2016 May 15;129(10):2075-84.

N/A

2016 

Sheng Z, **Yu L**, Zhang T, Pei X, Li X, Zhang Z and Du W. 
